---
title: "How to use workflowr"
output:
  html_document:
    toc: true
---

This is a website for quick satrt using workflowr. Contents are token from https://jdblischak.github.io/workflowr/articles/wflow-01-getting-started.html

***

## Installation and Configure Git (only need to do once per computer)
```{r eval=FALSE}
install.packages("workflowr")
library("workflowr")

wflow_git_config(user.name = "Jiangrong Ouyang", user.email = "jiangrongo@student.unimelb.edu.au")
```

## Start a new workflowr project
```{r eval=FALSE}
wflow_start("workflowr")
```
* This creates a directory called `workflowr/`. It also changes the working directory to `workflowr/`

* 2 required subdirectories are `analysis/` and `docs/`
 + `analysis/`: This directory contains all the source,
   R Markdown files for implementing the data analyses.
 + `docs/`: This directory contains all the HTML files,
   The HTML files are built from the R Markdown files in `analysis/`

## Build the website
* Currently, `docs/` directory is empty because we have not yet generated the website from the `analysis/` files.

* To build the website, run the function `wflow_build()`. To view the site run `wflow_view()`
```{r eval=FALSE}
wflow_build()
wflow_view()
```


## Customize your site!  
   + Edit the R Markdown files in `analysis/`  
   + Edit the theme and layout in `analysis/_site.yml`  
   + Add new or copy existing R Markdown `files to analysis/`  
   + Re-build the HTML files and display them by `wflow_build()`  


## Publish the website  
   i.e. version the source code and HTML results
Now, the project is still local.  
To view the status of the workflowr project, run `wflow_status()`
```{r eval=FALSE}
wflow_status()
```

 * To publish your changes as part of your website, use `wflow_publish()`.

 * To commit your changes without publishing them yet, use `wflow_git_commit()`.

```{r eval=FALSE}
wflow_publish("analysis/*Rmd", "Start my new project")
wflow_status()  # view the status again
```


## Deploy the website
 * create repository on GitHub
 * tell local Git repository about this new GitHub repository
```{r eval=FALSE}
wflow_git_remote("origin", "jiangrongo", "workflowr")  
```

This creates the alias “origin” that points to **remote repository** on GitHub. **Only** need to run this command **once** to add the remote repository.  

* **Each time you make changes to your project: run `wflow_publish()`.
Then run `wflow_git_push()` to send the changes to GitHub.**

```{r eval=FALSE}
wflow_git_push(dry_run = TRUE)
wflow_git_push()
```
* dry_run = TRUE previews what the function will do  
 Remove this argument to actually push to GitHub.
 
+ if Error occur, push it in teriminal
`cd workflowr`  
`git push origin master`

***
